method

### 2021-10-05 06_Paper/ER-ED/method.Rmd
added questionnaires

Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
This survey contains a number of questionnaires.
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].

>>>>

Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
This survey contained a number of questionnaires:
General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
